### 2014-03-01 paper/real.tex
js, almost done

Unsurprisingly, our coarse-grained combined language approach has been
inspired by existing browser (security) architectures.
%
Browsers, for example, isolate pages of different origins by running
them in separate runtimes.
%
Similarly, they provide the Worker JS object~\tocite{}, which allows
JavaScript to execute code in separate threads with separate JS
runtimes (and fresh global objects).
%
In both cases, code relies on the \texttt{postMessage} message-passing
API for communication.\footnote{
  The message-passing approach is, in part, due to ECMAScript's lack
  of well-defined semantics for concurrency.
  %
  Hence sharing and accessing objects such as the DOM across Worker
  threads is undefined.
}

\Red{HERE}
Our |specLangJS roundrobinf| implementation builds on the existing
Worker implementat

Hence, our implementation provides

\begin{itemize}
\item not completely unrealist; workers provide a similar world; we
  provide labeled workers

\item actual embeddings of JS have external effects; consider the browser
  case as in SWAPI
\begin{itemize}
   \item associate label with browsing context ~ task
   \item use CSP and sandbox flags to control external effects
   \item mediate communication by interposing on on postMessage
   argue that browsers already have to provide isolation guarantees
   between different compartments
\end{itemize}

\item talk about SWAPI's attach object feature that makes the concrete
  implementation more interesting
\end{itemize}

Of course, applications, such as browsers, that embed JavaScript
expose various features that perform external effects (again by
attaching them as objects to the JS global object).
%

\cut{

\subsection{Example: JavaScript}
\label{sec:real:javascript}

(NB:\ the JS spec refers to execution context and state; when we refer to
execution context, we refer to both the context AND the state)

(Some background on JavaScript versus ECMAScript, since ECMAScript
constitutes the semantics we're actually going to combine with
IFC;\ everything else has to be locked down or made IFC-specific).

(Lay out how ECMAScript semantics work. Execution context and syntax.
Don't go into too much detail.  Point out that the execution context/state
corresponds implementation-wise to a JavaEngine)
g
(Minimal IFC fragment.  Actually, this wants to be in the general section.
So specialize this some more?)

(Combined ECMAScript and IFC. Talk about serialization. Draw parallel to web
workers, note the similarity.)
}

>>>>

Unsurprisingly, our coarse-grained combined language approach has been
inspired by existing browser (security) architectures.
%
Browsers, for example, isolate pages of different origins by running
them in separate runtimes.
%
Similarly, they provide the Worker JS object~\tocite{}, which allows
JavaScript to execute code in separate threads with separate JS
runtimes (and fresh global objects).
%
In both cases, code relies on the \texttt{postMessage} message-passing
API for communication, similar to our system.\footnote{
  The message-passing approach is, in part, due to ECMAScript's lack
  of well-defined semantics for concurrency.
  %
  Hence sharing and accessing objects such as the DOM across Worker
  threads is undefined.
}

More interestingly, the SWAPI implementation directly leverages these
mechanisms to implement the semantics of |specLangJS roundrobinf|
without modifying the JS runtime or intrusively changing the browser
layout engine~\tocite{}.
%
However, a simple implementation of just associating a label with
Workers and browsing context (iframes and top-level pages) to enforce
IFC on the executing JavaScript is not sufficient.
%
The initial global object of a Worker contains the
\texttt{XMLHttpRequest} (XHR) object, while the global object of a
browsing context additionally contains the DOM, i.e., the global
object in a browser JS runtime is not simply |tS0|, above, and thus,
in both cases, JS code can trivially leak information (e.g., to the
network with XHR or persistent storage using the DOM).
%

To address this we use content security policy (CSP) and (iframe)
sandbox~\tocite{} to restrict external effects according to the label
of a task (Worker or browsing context), as describe
in~\tocite{}.
%
Of course, simply disallowing all external effects for all browsing
contexts would break most of the Web.
%
Hence SWAPI only enforces IFC, and thus restricts external effects,
when the JS code uses the new API.\footnote{
  Once a piece of code ``opts-in'' to use our IFC API, in addition to
  restricting external effects we interpose ``standard''
  \texttt{postMessage} communication to ensure that no information is
  leaked between contexts that have opted-in and those that have not.
}
%
Moreover, rather than disallowing all external effects, SWAPI allows
controlled network communication by leveraging the fact that web
pages already have an accompanying security policy: the same origin
policy.
%
Hence, for example, a Worker that has read data only sensitive to
\texttt{http://bank.ch} can communicate with this domain; only once
\texttt{http://aws.com} data is also included in the context will all
network requests be blocked.
%
Of course, this requires that we use a concrete label format to
express the policies; we refer the interested reader to~\tocite{} for
more details.
